---
title: "Assignment"
author: "Raymond Looney"
date: "10/14/2020"
output: pdf_document
---

# Part A

## Question 1:

When we first sketched our graphs, Paulina took the approach of looking at what specifically impacts a person's opinion when considering to become a conservationist or not. Raymond looked at the entire system to explore which factors are making these decisions and impacting the socio-ecological system as a whole.

```{r}
require(png)
img <- readPNG('Paulina_diagram.png',native = T)
plot(NA,xlim=c(0,nrow(img)),ylim=c(0,ncol(img)),xaxt='n',yaxt='n',xlab='',ylab='')
rasterImage(img,0,0,nrow(img),ncol(img))
```

Figure 1: Paulina's diagram

```{r}
require(png)
img <- readPNG('Raymond_diagram.png',native = T)
plot(NA,xlim=c(0,nrow(img)),ylim=c(0,ncol(img)),xaxt='n',yaxt='n',xlab='',ylab='')
rasterImage(img,0,0,nrow(img),ncol(img))
```

Figure 2: Raymond's diagram

## Question 2:

When we came together to talk about what we did we both felt like Paulina did a great job added structure to the model which we used to build our final diagram. Raymond added all the extra bits and pieces that influence each mechanism indiviudally. After some painstaking drawing on an online software we were able to create the following diagram using both of our ideas.

```{r}
require(png)
img <- readPNG('Final_diagram.png',native = T)
plot(NA,xlim=c(0,nrow(img)),ylim=c(0,ncol(img)),xaxt='n',yaxt='n',xlab='',ylab='')
rasterImage(img,0,0,nrow(img),ncol(img))
```

Figure 3: Diagram consisting of Raymond and Paulina's ideas.

## Question 3:

```{r}
require(png)
img <- readPNG('Parameters.png',native = T)
plot(NA,xlim=c(0,nrow(img)),ylim=c(0,ncol(img)),xaxt='n',yaxt='n',xlab='',ylab='')
rasterImage(img,0,0,nrow(img),ncol(img))
```

``` {r coral}

require(deSolve)

# Initial values
state <- c(X = 0.5) #fraction of total population that are conservationists
times <- seq(0,100,by=0.1)

# Parameters
parameters <- c(k = 1.014,j = 1.68, s = 0.5, phi = 0.2, C = 0.1, P = 0.5)

# Model
consv <- function(t,state,parameters){
  with(as.list(c(state,parameters)),{
       dX <- k*X*(1-X)*(-1+j*(1-C)-s*P*(1-X)+phi*(2*X-1))
      list(c(dX))   
  })}

# Solve model and plot results 
out <- ode(y = state,times=times,func=consv,parms=parameters) 
par(mfrow=c(1,1))

plot(out[,1],out[,2],ylab='X',xlab='time',las=1)

```

(a) What are the long-term dynamics of the system with the default parameters given below?

(b) What are the most important parameters in determining long-term dynamics? 